Omix

### 2019-04-11 omix/omix.Rmd

```{r load_libraries}
library(circlize)
library(ComplexHeatmap)
library(crunch)
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(kableExtra)
library(naniar)
library(openxlsx)
library(reshape2)
library(tidyverse)
library(VennDiagram)

theme_set(theme_light())
```

@@

# DEPMAP/TCGA: Heatmaps

@@

## GE

@@

## CN

Data wrangling and processing:
```{r cn_heatmap_data, eval=FALSE, warning=FALSE}
# TCGA copy number
cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
# Melt
cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
# Average scaled TPM per gene per TCGA classification
cn_tcga_avg <- cn_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
# Make wide
cn_tcga_wide <- dcast(data = cn_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
rownames(cn_tcga_wide) <- cn_tcga_wide$Gene
cn_tcga_wide$Gene <- NULL
colnames(cn_tcga_wide) <- paste(colnames(cn_tcga_wide), "TCGA", sep = "_")

@@

Pseudo-figure caption: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project. Levels are -1 for copy number loss, 0 for neutral, and 1 for gain. In each dataset and for each TCGA classification, these numeric copy number levels across all genes shared between the two datasets were averaged, and the datasets were correlated against each other. Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.

Make heatmaps:
```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
col_fun <- colorRamp2(c(0, 0.25, 0.5, 0.75), c("black", "red3", "yellow", "white"))
cn_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")

# 18Q4
cn_ht4order <- Heatmap(cn_corr_wide, cluster_rows = FALSE)
cn_ht <- Heatmap(cn_corr_wide, 
                 name = "Copy number correlation",
                 col = col_fun, 
                 rect_gp = gpar(col = "black"),
                 heatmap_legend_param = cn_ht_legend_list,
                 row_order = rev(column_order(cn_ht4order)), 
                 show_column_dend = FALSE, 
                 cluster_rows = FALSE, 
                 row_names_side = "left",
                 row_title = "DepMap cancer cell lines",
                 column_title = "TCGA tumor samples", 
                 column_title_side = "bottom")
# png(filename = "./figures/cn_depmap_tcga_heatmap_pearson.png", width = 7.5, height = 8, units = "in", res = 500)
draw(cn_ht, heatmap_legend_side = "top")
# dev.off()
```

## Mut

Data wrangling and processing:
```{r mut_heatmap_data, eval=FALSE}
# TCGA
mut_tcga <- read.delim("./data/mutation/mutation_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
mut_tcga <- unfactorize(mut_tcga)
mut_tcga[, 4:ncol(mut_tcga)] <- apply(mut_tcga[, 4:ncol(mut_tcga)], 2, function(x) ifelse(x > 1, 1, x))
colnames(mut_tcga)[colnames(mut_tcga) == "cancer"] <- "TCGA_classification"
# Melt
mut_tcga_melt <- melt(mut_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_tcga)[4:length(colnames(mut_tcga))], variable.name = "Gene", value.name = "Mutation_Status")
# Average CN levels per gene per TCGA classification
mut_tcga_prop <- mut_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
# Make wide
mut_tcga_wide <- dcast(data = mut_tcga_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
rownames(mut_tcga_wide) <- mut_tcga_wide$Gene
mut_tcga_wide$Gene <- NULL
colnames(mut_tcga_wide) <- paste(colnames(mut_tcga_wide), "TCGA", sep = "_")

# DepMap
mut_depmap <- read.delim("./data/mutation/mutation_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
mut_depmap <- unfactorize(mut_depmap)
mut_depmap[, 4:ncol(mut_depmap)] <- apply(mut_depmap[, 4:ncol(mut_depmap)], 2, function(x) ifelse(x > 1, 1, x))
colnames(mut_depmap)[colnames(mut_depmap) == "cancer"] <- "TCGA_classification"
# Melt
mut_depmap_melt <- melt(mut_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_depmap)[4:length(colnames(mut_depmap))], variable.name = "Gene", value.name = "Mutation_Status")
# Average CN levels per gene per TCGA classification
mut_depmap_prop <- mut_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
# Make wide
mut_depmap_wide <- dcast(data = mut_depmap_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
rownames(mut_depmap_wide) <- mut_depmap_wide$Gene
mut_depmap_wide$Gene <- NULL
colnames(mut_depmap_wide) <- paste(colnames(mut_depmap_wide), "DepMap", sep = "_")

@@

Pseudo-figure caption: This is comparison of binary gene-level mutation frequency profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project. In each dataset and for each TCGA classification, the proportion of samples containing at least one mutation was calculated for all genes shared between the two datasets, and the proportions were correlated against each other. Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.

Genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutaiton in at least one cancer cell line from DepMap.

Make heatmaps:
```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
col_fun <- colorRamp2(c(0, 0.15, 0.35, 0.5), c("black", "red3", "yellow", "white"))
mut_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")

# 18Q4
mut_ht4order <- Heatmap(mut_corr_wide, cluster_rows = FALSE)
mut_ht <- Heatmap(mut_corr_wide, 
                 name = "Mutation correlation",
                 col = col_fun, 
                 rect_gp = gpar(col = "black"),
                 heatmap_legend_param = mut_ht_legend_list,
                 row_order = rev(column_order(mut_ht4order)), 
                 show_column_dend = FALSE, 
                 cluster_rows = FALSE, 
                 row_names_side = "left",
                 row_title = "DepMap cancer cell lines",
                 column_title = "TCGA tumor samples", 
                 column_title_side = "bottom")
# png(filename = "./figures/mut_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
draw(mut_ht, heatmap_legend_side = "top")
# dev.off()
```

>>>>

```{r load_libraries}
library(circlize)
library(ComplexHeatmap)
library(crunch)
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(kableExtra)
library(lemon)
library(naniar)
library(openxlsx)
library(reshape2)
library(tidyverse)
library(VennDiagram)

theme_set(theme_light())
# install.packages("lemon")
```

@@

# DEPMAP/TCGA

@@

```{r}
tcga_classifications_16 <- c("BLCA", "BRCA", "COADREAD", "ESCA", "GBMLGG", "HNSC", "KIRC", "LIHC", "LUAD", "LUSC", "OV", "PAAD", "SARC", "SKCM", "STAD", "UCEC")
```

## Heatmaps

### GE

@@

### CN

Continuous CN estimate data wrangling and processing:
```{r cn_heatmap_data_continuous, eval=FALSE, warning=FALSE}
# DepMap copy number
cn_depmap <- read.delim("./../../htscreens_giant_files/omix/CN/CN_cont_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
# Mean center scale
cn_depmap[, 4:ncol(cn_depmap)] <- apply(cn_depmap[, 4:ncol(cn_depmap)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
# Melt
cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN_scaled")
cn_depmap_melt <- filter(cn_depmap_melt, TCGA_classification %in% tcga_classifications_16)
# Average scaled TPM per gene per TCGA classification
cn_depmap_avg <- cn_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN_scaled))
# Make wide
cn_depmap_wide <- dcast(data = cn_depmap_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
rownames(cn_depmap_wide) <- cn_depmap_wide$Gene
cn_depmap_wide$Gene <- NULL
colnames(cn_depmap_wide) <- paste(colnames(cn_depmap_wide), "DepMap", sep = "_")

# TCGA cop number
cn_tcga <- read.delim("./../../htscreens_giant_files/omix/CN/CN_cont_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
# Mean center scale
cn_tcga[, 4:ncol(cn_tcga)] <- apply(cn_tcga[, 4:ncol(cn_tcga)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
# Melt
cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN_scaled")
cn_tcga_melt <- filter(cn_tcga_melt, TCGA_classification %in% tcga_classifications_16)
# Average scaled TPM per gene per TCGA classification
cn_tcga_avg <- cn_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN_scaled))
# Make wide
cn_tcga_wide <- dcast(data = cn_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
rownames(cn_tcga_wide) <- cn_tcga_wide$Gene
cn_tcga_wide$Gene <- NULL
colnames(cn_tcga_wide) <- paste(colnames(cn_tcga_wide), "TCGA", sep = "_")

# Correlate all against all
cn_wide <- bind_cols(cn_depmap_wide, cn_tcga_wide)
cn_corr <- cn_wide %>% as.matrix %>% cor(method = "pearson") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
# Filter self-comparisons and eliminate duplicate correlations
cn_corr <- filter(cn_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
# Data management
colnames(cn_corr) <- c("DepMap", "TCGA", "r")
cn_corr <- data.frame(apply(cn_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
cn_corr$r <- as.numeric(as.character(cn_corr$r))
# cn_corr <- filter(cn_corr, DepMap %in% tcga_classifications_16 & TCGA %in% tcga_classifications_16)
# Set up coprrelation dataframe for plotting
cn_corr_wide <- dcast(cn_corr, DepMap ~ TCGA)
rownames(cn_corr_wide) <- cn_corr_wide$DepMap
cn_corr_wide$DepMap <- NULL
```

Thresholded CN estimate data wrangling and processing:
```{r cn_heatmap_data_thresholded, eval=FALSE, warning=FALSE}
# TCGA copy number
cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
# Melt
cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
# Average scaled TPM per gene per TCGA classification
cn_tcga_avg <- cn_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
# Make wide
cn_tcga_wide <- dcast(data = cn_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
rownames(cn_tcga_wide) <- cn_tcga_wide$Gene
cn_tcga_wide$Gene <- NULL
colnames(cn_tcga_wide) <- paste(colnames(cn_tcga_wide), "TCGA", sep = "_")

@@

Pseudo-figure caption for thresholded data: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project. Levels are -1 for copy number loss, 0 for neutral, and 1 for gain. In each dataset and for each TCGA classification, these numeric copy number levels across all genes shared between the two datasets were averaged, and the datasets were correlated against each other. Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.

Make heatmaps:
```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
col_fun <- colorRamp2(c(-0.5, 0, 0.25, 0.75), c("black", "red3", "yellow", "white"))
cn_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")

# 18Q4
cn_ht4order <- Heatmap(cn_corr_wide, cluster_rows = FALSE)
cn_ht <- Heatmap(cn_corr_wide, 
                 name = "Copy number correlation",
                 col = col_fun, 
                 rect_gp = gpar(col = "black"),
                 heatmap_legend_param = cn_ht_legend_list,
                 row_order = rev(column_order(cn_ht4order)), 
                 show_column_dend = FALSE, 
                 cluster_rows = FALSE, 
                 row_names_side = "left",
                 row_title = "DepMap cancer cell lines",
                 column_title = "TCGA tumor samples", 
                 column_title_side = "bottom")
# png(filename = "./figures/cn_depmap_tcga_heatmap_pearson_continuous.png", width = 7.5, height = 8, units = "in", res = 500)
draw(cn_ht, heatmap_legend_side = "top")
# dev.off()
```

### Mut

Data wrangling and processing:
```{r mut_heatmap_data, eval=FALSE}
# TCGA
mut_tcga <- read.delim("./data/mutation/mutation_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
mut_tcga <- unfactorize(mut_tcga)
mut_tcga[, 4:ncol(mut_tcga)] <- apply(mut_tcga[, 4:ncol(mut_tcga)], 2, function(x) ifelse(x > 1, 1, x))
colnames(mut_tcga)[colnames(mut_tcga) == "cancer"] <- "TCGA_classification"
# Melt
mut_tcga_melt <- melt(mut_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_tcga)[4:length(colnames(mut_tcga))], variable.name = "Gene", value.name = "Mutation_Status")
# Calce proportion mutated per gene per TCGA classification
mut_tcga_prop <- mut_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status) / n())
# Make wide
mut_tcga_wide <- dcast(data = mut_tcga_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
mut_tcga_wide <- mut_tcga_wide[mut_tcga_wide$Gene != "TP53", ]
rownames(mut_tcga_wide) <- mut_tcga_wide$Gene
mut_tcga_wide$Gene <- NULL
colnames(mut_tcga_wide) <- paste(colnames(mut_tcga_wide), "TCGA", sep = "_")

# DepMap
mut_depmap <- read.delim("./data/mutation/mutation_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
mut_depmap <- unfactorize(mut_depmap)
mut_depmap[, 4:ncol(mut_depmap)] <- apply(mut_depmap[, 4:ncol(mut_depmap)], 2, function(x) ifelse(x > 1, 1, x))
colnames(mut_depmap)[colnames(mut_depmap) == "cancer"] <- "TCGA_classification"
# Melt
mut_depmap_melt <- melt(mut_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_depmap)[4:length(colnames(mut_depmap))], variable.name = "Gene", value.name = "Mutation_Status")
# Calce proportion mutated per gene per TCGA classification
mut_depmap_prop <- mut_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status) / n())
# Make wide
mut_depmap_wide <- dcast(data = mut_depmap_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
mut_depmap_wide <- mut_depmap_wide[mut_depmap_wide$Gene != "TP53", ]
rownames(mut_depmap_wide) <- mut_depmap_wide$Gene
mut_depmap_wide$Gene <- NULL
colnames(mut_depmap_wide) <- paste(colnames(mut_depmap_wide), "DepMap", sep = "_")

@@

Pseudo-figure caption: This is comparison of binary gene-level mutation frequency profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project. In each dataset and for each TCGA classification, the proportion of samples containing at least one mutation was calculated for all genes shared between the two datasets, and the proportions were correlated against each other. Pearson/Spearman correlations (r) between TCGA and DepMap mutation feature sets are shown in the heatmap.

For plots labeled as "5000", the 5,000 mosr variable genes analyzed in the gene expression heatmap were selected for the mutation analyses. Alternatively, for the plots labeled as "252", the genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutation in at least one cancer cell line from DepMap. TP53 was removed from the heatmap, as was done in Barretina et al. (2012). For the scatterplots, TP53 was retained.

Make heatmaps:
```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
col_fun <- colorRamp2(c(0, 0.2, 0.5, 0.7), c("black", "red3", "yellow", "white"))
mut_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")

# 18Q4
mut_ht4order <- Heatmap(mut_corr_wide, cluster_rows = FALSE)
mut_ht <- Heatmap(mut_corr_wide,
                 name = "Mutation correlation",
                 col = col_fun, 
                 rect_gp = gpar(col = "black"),
                 heatmap_legend_param = mut_ht_legend_list,
                 row_order = rev(column_order(mut_ht4order)), 
                 show_column_dend = FALSE, 
                 cluster_rows = FALSE, 
                 row_names_side = "left",
                 row_title = "DepMap cancer cell lines",
                 column_title = "TCGA tumor samples", 
                 column_title_side = "bottom")
# png(filename = "./figures/mut_depmap_tcga_heatmap_spearman_252.png", width = 7.5, height = 8, units = "in", res = 500)
draw(mut_ht, heatmap_legend_side = "top")
# dev.off()
```

## Scatterplots

### CN

```{r cn_scatters_data, eval=FALSE}
# For both datasets: CN_Status encoded as 1 is non-neutral (-1 or +1) and 0 is neutral

# TCGA
# Calc proportion of non-neutral CN per gene per TCGA classification
cn_tcga_prop <- cn_tcga_melt
cn_tcga_prop$CN_Status <- with(cn_tcga_prop, ifelse(CN != 0, 1, CN))
cn_tcga_prop <- cn_tcga_prop %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_NonNeutral_CN = sum(CN_Status) / n(), N = n())

# DepMap
# Calc proportion of non-neutral CN per gene per TCGA classification
cn_depmap_prop <- cn_depmap_melt
cn_depmap_prop$CN_Status <- with(cn_depmap_prop, ifelse(CN != 0, 1, CN))
cn_depmap_prop <- cn_depmap_prop %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_NonNeutral_CN = sum(CN_Status) / n(), N = n())

# Merge non-neutral CN proportion dataframes for plotting
cn_props <- merge(cn_depmap_prop, cn_tcga_prop, by = c("TCGA_classification", "Gene"), all = TRUE, suffixes = c("_DepMap","_TCGA"))
```

Pseudo-caption: This is a comparison of proportions of non-neutral copy number samples between cancer cell lines and TCGA samples in our 16 TCGA classification categories. Each point corresponds to a single gene in the associated cancer type. For these plots, thresholded copy number levels of -1 (loss) and +1 (gain) were recoded as "non-neutral."

```{r cn_scatters, fig.height=8, fig.width=8, eval=FALSE}
cn_props_scatters <- ggplot(data = cn_props, aes(x = Proportion_NonNeutral_CN_TCGA, y = Proportion_NonNeutral_CN_DepMap)) +
  facet_wrap(~ TCGA_classification, nrow = 4) +
  geom_point(alpha = 0.3, color = "darkcyan") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, color = "darkgray") +
  stat_cor(method = "pearson", label.x = 0.85, label.y = 0.15, label.sep = "\n") +
  # geom_text_repel(data = subset(cn_props, Proportion_NonNeutral_CN_TCGA > 0.4 & Proportion_NonNeutral_CN_DepMap > 0.6), aes(x = Proportion_NonNeutral_CN_DepMap, y = Proportion_NonNeutral_CN_DepMap, label = Gene), size = 3) +
  labs(x = "TCGA non-neutral CN frequency", y = "DepMap non-neutral CN frequency", caption = paste0(formatC(x = length(unique(cn_props$Gene)), format = "d", big.mark = ","), " genes compared."))

ggsave("./figures/cn_depmap_tcga_scatter_pearson.png", cn_props_scatters, device = "png", dpi = 450, width = 12, height = 12, units = "in")
```

### Mut

```{r mut_scatters_data, eval=FALSE}
# Merge mutation proportion dataframes for plotting
mut_props <- merge(mut_depmap_prop, mut_tcga_prop, by = c("TCGA_classification", "Gene"), all = TRUE, suffixes = c("_DepMap","_TCGA"))
```

Pseudo-caption: This is a comparison of proportions of mutated samples between cancer cell lines and TCGA samples in our 16 TCGA classification categories. Each point corresponds to a single gene in the associated cancer type.

```{r mut_scatters, fig.height=8, fig.width=8, eval=FALSE}
mut_props_scatters <- ggplot(data = mut_props, aes(x = Proportion_Mut_TCGA, y = Proportion_Mut_DepMap)) +
  facet_wrap(~ TCGA_classification, nrow = 4) +
  geom_point(alpha = 0.3, color = "darkcyan") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, color = "gainsboro") +
  stat_cor(method = "pearson", label.x = 0.85, label.y = 0.15, label.sep = "\n") +
  geom_text_repel(data = subset(mut_props, Proportion_Mut_TCGA > 0.3 & Proportion_Mut_DepMap > 0.3), aes(x = Proportion_Mut_TCGA, y = Proportion_Mut_DepMap, label = Gene), size = 3) +
  labs(x = "TCGA mutation frequency", y = "DepMap mutation frequency", caption = paste0(formatC(x = length(unique(mut_props$Gene)), format = "d", big.mark = ","), " genes compared."))

ggsave("./figures/mut_depmap_tcga_scatter_pearson.png", mut_props_scatters, device = "png", dpi = 450, width = 12, height = 12, units = "in")
```
